|

### 2018-11-02 paper.Rmd
Added README.

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 4 input files I created (see below) from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing).

@@

# Basics: Input and output files
All the files you need to produce the present PDF file are 4 input files...

>>>>

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files I created --- `paper.rmd`, `header.tex`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). Ignore the other files.

@@

# Basics: Input and output files
All the files you need to produce the present PDF file are the input files...

### 2018-11-02 paper.tex
Added README.

\begin{itemize}
\item
  \ldots{}download the 4 input files I created (see below) from
  \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this
  folder}.
\item
  \ldots{}learn R and read about the other underlying components namely
  \href{https://en.wikipedia.org/wiki/Markdown}{Markdown},
  \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and
  \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

All the files you need to produce the present PDF file are 4 input
files\ldots{}

>>>>

\begin{itemize}
\item
  \ldots{}download the 5 input files I created --- \texttt{paper.rmd},
  \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and
  \texttt{american-sociological-association.csl} --- from
  \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this
  folder}. Ignore the other files.
\item
  \ldots{}learn R and read about the other underlying components namely
  \href{https://en.wikipedia.org/wiki/Markdown}{Markdown},
  \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and
  \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

All the files you need to produce the present PDF file are the input
files\ldots{}
